Probabilistic Programming

### 2014-04-21 paper/paper.tex
Update paper.tex

We encode the structure of an AST as a probabilistic model. The model is a data
structure that maps node paths to probability distributions of node types or
values. A node path is a list of node types and relationships that encodes the
unique position of a node in a program's AST. The probability distribution for a
node path is the set of possible node types or values that would appear in the
syntax tree following the given path, and the respective probabilities of their
occurance following the given path.

>>>>

We encode the structure of an AST as a probabilistic model. The model is a data
structure that maps node paths to probability distributions of node types or
values. A node path is a list of node types and relationships that encodes the
unique position of a node in a program's AST. The probability distribution for a
node path is the set of possible node types or values that would appear in the
syntax tree following the given path, and the respective probabilities of their
occurrence following the given path.
